Finding Quality Issues in SKOS Vocabularies

### 2012-03-26 analysis.tex
added mil for mesh

\textbf{Vocabulary} & \rotatebox{90}{\textbf{Abbreviation}} & \rotatebox{90}{\textbf{Version/last mod.}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Auth. Concepts}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} \\
\toprule
Agricultural Thesaurus & \textbf{AGROVOC} & 1.3 & 32,035 & 32,035 & 620,629 & 65,934 & 32,085 & 1 \\
\hline
DBpedia Categories & \textbf{DBpedia} & ? & 743,410 & 743,410 & 740,352 & 1,490,316 & 0 & 0 \\
\hline
The EU's multilingual thesaurus & \textbf{Eurovoc} & 5.0 & 6,797 & 6,797 & 457,788 & 18,491 & 15,512 & 128 \\
\hline
Geonames Ontology & \textbf{Geonames} & 2.2.1 & 671 & 671 & 671 & 0 & 671 & 9 \\
\hline
Gemeenschappelijke Thesaurus Audiovisuele Archieven & \textbf{GTAA} & 2010/08/25 & 171,991 & 171,991 & 178,776 & 50,892 & 343,980 & 9 \\
\hline
Integrated Public Sector Vocabulary & \textbf{IPSV} & 2.00 & 4,732 & 3,080 & 7,945 & 13,843 & 4,483 & 3 \\
\hline
Library of Congress Subject Headings & \textbf{LCSH} & 2011/08/09 & 459,182 & 407,908 & 746,076 & 595,754 & 815,816 & 19 \\
\hline
Austrian Armed Forces Thesaurus & \textbf{LVAk} & n/a & 13,411 & 13,411 & 17,250 & 16,346 & 0 & 0 \\
\hline
Middle Kingdom tombs of Ancient Egypt Thesaurus & \textbf{Meketre} & 2011/07/07 & 422 & 422 & 569 & 1,698 & 6 & 2 \\
\hline
Medical Subject Headings & \textbf{MeSH} & ? & 24,626 & 24,626 & 150,617 & 38,858 & 0 & 0 \\
\hline
North American Industry Classification System & \textbf{NAICS} & 2012 & 4,175 & 2,213 & 0 & 8,684 & 2,235 & 1 \\
\hline
New York Times People & \textbf{NYTP} & 2010/06/22 & 4,979 & 4,979 & 4,979 & 0 & 4,979 & 1 \\
\hline
University of Southampton Pressinfo & \textbf{Pressinfo} & 2011/02/24 & 1,125 & 1,125 & 0 & 0 & 0 & 0 \\
\hline
Peroxisome Knowledge Base & \textbf{PXV} & 1.6 & 2,112 & 1,686 & 3,628 & 2,695 & 1,716 & 1 \\
\hline
Thesaurus for Economics & \textbf{STW} & 8.06 & 6,524 & 6,524 & 31,189 & 57,907 & 6,531 & 1 \\
\bottomrule
\end{tabular}

@@

Missing In-Links & 171,980* & 19 && 1,686 & 6,796 & 3,080 & 32,035 & 733,800* & 1,125 & 20 & 404,540* & 422 & 6,516 & 2,213 & 13,411 \\

Missing Out-Links & 171,991 & 671 && 1,472 & 6,797 & 0 & 32,035 & 743,410 & 1,116 & 0 & 408,198 & 273 & 6,524 & 0 & 13,411 \\

@@

% Structural Issues
It could be observed that vocabularies that contain person or location names (GTAA and Geonames) have more orphan concepts than other vocabularies, establishing a network of terms in a specific domain (e.g., STW). Regarding weakly connected components, we see that those vocabularies that only consist of orphan concepts, contain no weakly connected components. Three vocabularies have one weakly connected component which means that there is one ``giant component''. All other vocabularies split into several ``islands'' of semantically related concepts. Hierarchical cycles are observed not to be a common issue, however they affect DBpedia to a great extent \todo{CM}{reason?}. Valueless associative relations occur in 9 vocabularies, with their total number being relatively low compared to the total number of all semantic relations in the respective vocabularies. GTAA, Geonames, and NYTP have no top concept defined for any of the concept schemes they use. Eurovoc uses 128 concept schemes but only one without top concept. The opposite situation can be observed for LCSH which uses 19 concept schemes, but only one has a top concept. Only PXV vocabulary is affected by top concepts having broader concept in the current version. In an earlier version a different concept causing this issue could be spotted. According to the vocabulary creator it was an abaondoned concept, still available in the triplestore but maybe introduced by some bug in the vocabulary management software.

>>>>

\textbf{Vocabulary} & \rotatebox{90}{\textbf{Abbreviation}} & \rotatebox{90}{\textbf{Version/Year}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Auth. Concepts}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} \\
\toprule
Agricultural Thesaurus & \textbf{AGROVOC} & 1.3 & 32,035 & 32,035 & 620,629 & 65,934 & 32,085 & 1 \\
\hline
DBpedia Categories & \textbf{DBpedia} & 3.7 & 743,410 & 743,410 & 740,352 & 1,490,316 & 0 & 0 \\
\hline
The EU's multilingual thesaurus & \textbf{Eurovoc} & 5.0 & 6,797 & 6,797 & 457,788 & 18,491 & 15,512 & 128 \\
\hline
Geonames Ontology & \textbf{Geonames} & 2.2.1 & 671 & 671 & 671 & 0 & 671 & 9 \\
\hline
Gemeenschappelijke Thesaurus Audiovisuele Archieven & \textbf{GTAA} & 2010/08/25 & 171,991 & 171,991 & 178,776 & 50,892 & 343,980 & 9 \\
\hline
Integrated Public Sector Vocabulary & \textbf{IPSV} & 2.00 & 4,732 & 3,080 & 7,945 & 13,843 & 4,483 & 3 \\
\hline
Library of Congress Subject Headings & \textbf{LCSH} & 2011/08/09 & 459,182 & 407,908 & 746,076 & 595,754 & 815,816 & 19 \\
\hline
Austrian Armed Forces Thesaurus & \textbf{LVAk} & n/a & 13,411 & 13,411 & 17,250 & 16,346 & 0 & 0 \\
\hline
Middle Kingdom tombs of Ancient Egypt Thesaurus & \textbf{Meketre} & 2011/07/07 & 422 & 422 & 569 & 1,698 & 6 & 2 \\
\hline
Medical Subject Headings & \textbf{MeSH} & 2006 & 24,626 & 24,626 & 150,617 & 38,858 & 0 & 0 \\
\hline
North American Industry Classification System & \textbf{NAICS} & 2012 & 4,175 & 2,213 & 0 & 8,684 & 2,235 & 1 \\
\hline
New York Times People & \textbf{NYTP} & 2010/06/22 & 4,979 & 4,979 & 4,979 & 0 & 4,979 & 1 \\
\hline
University of Southampton Pressinfo & \textbf{Pressinfo} & 2011/02/24 & 1,125 & 1,125 & 0 & 0 & 0 & 0 \\
\hline
Peroxisome Knowledge Base & \textbf{PXV} & 1.6 & 2,112 & 1,686 & 3,628 & 2,695 & 1,716 & 1 \\
\hline
Thesaurus for Economics & \textbf{STW} & 8.06 & 6,524 & 6,524 & 31,189 & 57,907 & 6,531 & 1 \\
\bottomrule
\end{tabular}

@@

Missing In-Links & 171,980* & 19 & 24625 & 1,686 & 6,796 & 3,080 & 32,035 & 733,800* & 1,125 & 20 & 404,540* & 422 & 6,516 & 2,213 & 13,411 \\

Missing Out-Links & 171,991 & 671 & 24626 & 1,472 & 6,797 & 0 & 32,035 & 743,410 & 1,116 & 0 & 408,198 & 273 & 6,524 & 0 & 13,411 \\

@@

% Structural Issues
It could be observed that vocabularies that contain person or location names (GTAA and Geonames) have more orphan concepts than other vocabularies, establishing a network of terms in a specific domain (e.g., STW). Regarding weakly connected components, we see that those vocabularies that only consist of orphan concepts, contain no weakly connected components. Three vocabularies have one weakly connected component which means that there is one ``giant component''. All other vocabularies split into several ``islands'' of semantically related concepts. Hierarchical cycles are observed not to be a common issue, however they affect DBpedia to a great extent because for some reason many of the concepts are related broader to themselves. Valueless associative relations occur in 9 vocabularies, with their total number being relatively low compared to the total number of all semantic relations in the respective vocabularies. GTAA, Geonames, and NYTP have no top concept defined for any of the concept schemes they use. Eurovoc uses 128 concept schemes but only one without top concept. The opposite situation can be observed for LCSH which uses 19 concept schemes, but only one has a top concept. Only PXV vocabulary is affected by top concepts having broader concept in the current version. In an earlier version a different concept causing this issue could be spotted. According to the vocabulary creator it was an abaondoned concept, still available in the triplestore but maybe introduced by some bug in the vocabulary management software.
